Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-03 draft/accordionComplexSurfaces.tex
More about the countercurrent order.

\begin{definition}
Consider an arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$.
Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}
\pierreguy{I need to modify these two definitions.}

>>>>

\begin{definition}
For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}
\pierreguy{Add a picture here?}

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
\pierreguy{Add picture.}
\end{remark}

For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, we denote by~$F_\alpha$ the set of walks of~$F$ marked at an occurence of~$\alpha^\pm$.

\begin{lemma}
\label{lemm:countercurrentOrderIsTotal}
For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
\end{lemma}
\begin{proof}
 The proof of \cite[Lemma 2.21]{PaluPilaudPlamondon} applies here.
\end{proof}

\begin{lemma}
\label{lemm:facesHaveMaximalElement}
For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rema:countercurrentOrderOnSurface}.

 {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
\end{proof}
